---
title: "Elements of Statistical Learning"
author: "Junrui Di"
output:
  pdf_document:
    toc: yes
---


# Chapter 2. Overview of Supervised Learning

```{r,child = 'Chap2.Rmd'}
```

\newpage

# Chapter 3: Linear Methods for Regression
```{r,child = 'Chap3.Rmd'}
```

\newpage

# Chapter 4: Linear Methodsfor Classification
```{r,child = 'Chap4.Rmd'}
```

\newpage

# Chapter 5: Basis Expansions and Regularization
```{r,child = 'Chap5.Rmd'}
```

\newpage

# Chapter 6: Kernel Smoothing Method
```{r,child = 'Chap6.Rmd'}
```

\newpage

# Chapter 7: Model Assessment and Selection
```{r,child = 'Chap7.Rmd'}
```

\newpage

# Chapter 8: Model Inference and Averaging
```{r,child = 'Chap8.Rmd'}
```

\newpage

# Chapter 9: Additive Models, Trees, and Related Methods
```{r,child = 'Chap9.Rmd'}
```

\newpage

# Chapter 10: Boosting and Addtive Trees
```{r,child = 'Chap10.Rmd'}
```

\newpage

# Chapter 11: Neural Networks
```{r,child = 'Chap11.Rmd'}
```

\newpage

# Chapter 12: Support Vector Machines and Flexible Discriminants
```{r,child = 'Chap12.Rmd'}
```

\newpage

# Chapter 13: Prototype Methods and Nearest-Neighbors
```{r,child = 'Chap13.Rmd'}
```

\newpage

# Chapter 14: Unsupervised Learning
```{r,child = 'Chap14.Rmd'}
```

\newpage

# Chapter 15: Random Forests
```{r,child = 'Chap15.Rmd'}
```

\newpage

# Chapter 16: Ensemble Learning
```{r,child = 'Chap16.Rmd'}
```

\newpage

# Chapter 17: Undirected Graphical Models
```{r,child = 'Chap17.Rmd'}
```

\newpage

# Chapter 18: High-Dimensional Problems: $p>>N$
```{r,child = 'Chap17.Rmd'}
```
